{\bf Practical Concurrency Testing}

### 2016-04-29 proposal/thesprop.tex
write some background text

\begin{dedication}
	For my dog, Louie.
\end{dedication}

@@

Most commonly, a programmer searches for concurrency bugs in her code by running it many times (in parallel, in serial, or both),
hoping that eventually, it will run according to the particular interleaving required to expose a hypothetical bug.
This technique, known as {\em stress testing}, is unreliable,
providing no guarantee of finding the failing interleaving in any finite amount of time, even when a bug does exist.
It also provides no assurance of correctness:
when finished, there is no way of knowing how much of the space of possible thread interleavings was actually tested.
%it may by chance test only a single interleaving over and over again!
Nevertheless, stress testing remains popular because of how easily a programmer can use it:
she simply wraps her program in a loop, sets it to run overnight, and kills it if her patience runs out before it finds a bug.

@@

Another problem stateless model checking suffers is that certain types of programs cannot be tested without the programmer putting forth some manual instrumentation effort.
For example, operating system kernels implement their own sources of concurrency and their own synchronization primitives,
so the checker needs to be told how to identify and control the execution of each thread.
Some expert programmers may be willing to add manual annotations to their code,
if they are already veteran concurrency research wizards,
but required manual effort is a serious downside for anyone with a looming deadline,
and especially so for students who are still learning basic concurrency principles.
%We should not expect programmers to add effortful manual annotations to their code,
%or they will abandon our fancy technique to instead simply run stress tests until their deadline tomorrow evening.

@@

>>>>

%\begin{dedication}
%	For my dog, Louie.
%\end{dedication}

@@

Most commonly, a programmer searches for concurrency bugs in her code by running it many times (in parallel, in serial, or both),
hoping that eventually, it will run according to the particular interleaving required to expose a hypothetical bug.
This technique, known as {\em stress testing}, is unreliable,
providing no guarantee of finding the failing interleaving in any finite amount of time.
%, even when a bug does exist.
It also provides no assurance of correctness:
when finished, there is no way of knowing how much of the space of possible thread interleavings was actually tested.
%it may by chance test only a single interleaving over and over again!
Nevertheless, stress testing remains popular because of how easily a programmer can use it:
she simply wraps her program in a loop, sets it to run overnight, and kills it if her patience runs out before it finds a bug.

@@

Another problem stateless model checking suffers is that certain types of programs cannot be tested without the programmer putting forth some manual instrumentation effort.
For example, operating system kernels implement their own sources of concurrency and their own synchronization primitives,
so the checker needs to be told how to identify and control the execution of each thread.
Some expert concurrency research wizards may be willing to add manual annotations to their code,
but required manual effort is a serious downside for anyone with a looming deadline,
and especially so for students who are still learning basic concurrency principles.
%We should not expect programmers to add effortful manual annotations to their code,
%or they will abandon our fancy technique to instead simply run stress tests until their deadline tomorrow evening.

@@

\input{overview}
